\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
phone nits

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system for parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
% a source-to-source shell compiler and associated runtime library
Given a script, \sys converts it to a dataflow graph, performs a series of transformations that expose parallelism while preserving its sequential semantics, and then converts the dataflow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
A lightweight annotation language allows command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands---two large and commonly used groups---guides the annotation language and optimized aggregator library that \sys uses.
% \kk{eurosys: Can we extend this to say that PaSh automatically uses constructs from this library? Otherwise it sounds like the user has to use it to make their scripts parallel.}
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation over 44 unmodified \unix scripts shows significant speedups ($0.98$--$61.1\times$, avg: $6.7\times$) stemming from the combination of its program transformations and runtime primitives.
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).
\end{abstract}

@@

We evaluate \sys 44 unmodified scripts including:
  (i) a series of benchmarks, ranging from classic \unix one-liners to modern data-processing scripts;
  (ii) two large and complex use cases for temperature analysis and web indexing;
%% , and container orchestration;
and 
  (iii) two micro-benchmarks inspired by (and comparing with) possible alternatives.
Speedups range between 0.98--61.1$\times$ (avg: $6.7\times$), with the 39 out of 44 scripts seeing non-trivial speedups. 
\sys's runtime primitives add to the base speedup extracted by \sys's program transformations---\eg 13.24$\times$ over a base 9.35$\times$ average for 10 representative \unix one-liners.
%  with \ttt{--width=64}, 
% \kk{eurosys: Readers don't know what --width is here so it might make sense to not mention it.}
% \sys performs better than \ttt{sort --parallel}, a hand-tuned parallel implementation, and GNU parallel, which returns incorrect results if used without care.
\sys accelerates a large program for temperature analysis by 2.52$\times$, parallelizing both the computation and the preprocessing fragment (\ie data download, extraction, and cleanup), which traditionally falls outside of the focus of conventional parallelization systems---even though it takes $75\%$ of the total execution time.
  % extracting 12.31$\times$ from the portion of the program that traditionally falls outside the focus of conventional parallelization systems.
  % \kk{\sys parallelizes the computation by 12.31 and not the preprocessing. It parallelizes the preprocessing by 2.}

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_example2.pdf}}
\begin{minted}[fontsize=\footnotesize,escapeinside=()]{bash}
mkfifo $t{0,1...}
curl $base/$y > $t0 & cat $t0 | split $t1 $t2 &
cat $t1 | xargs -n1 curl -s >$t3 & 
cat $t2 | xargs -n1 curl -s >$t4 &
...
cat $t9 | sort -rn > $t11 & cat $t10 | sort -rn > $t12 &
cat $t11 | eager > $t13 & cat $t12 | eager > $t14 &
sort -mrn $t13 $t14 > $t15 &
cat $t15 | head -n1 > $out1 &
wait $! && get-pids | xargs -n 1 kill -SIGPIPE
\end{minted}
\caption{
  \textbf{Output of \ttiny{pash --width=2} for Fig.~\ref{fig:example} (fragment).}
  \sys orchestrates parallel execution through named pipes, parallel operators, and custom runtime primitives---\eg \ttiny{eager}, \ttiny{split}, and \ttiny{get-pids}.
}
\vspace{-15pt}
\label{fig:example2}
\end{figure}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system for parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
% a source-to-source shell compiler and associated runtime library
Given a script, \sys converts it to a dataflow graph, performs a series of transformations that expose parallelism while preserving its sequential semantics, and then converts the dataflow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
A lightweight annotation language allows command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands---two large and commonly used groups---guides the annotation language and optimized aggregator library that \sys uses.
% \kk{eurosys: Can we extend this to say that PaSh automatically uses constructs from this library? Otherwise it sounds like the user has to use it to make their scripts parallel.}
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation over 44 unmodified \unix scripts shows significant speedups ($0.89$--$61.1\times$, avg: $6.7\times$) stemming from the combination of its program transformations and runtime primitives.
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).
\end{abstract}

@@

We evaluate \sys on 44 unmodified scripts including:
  (i) a series of benchmarks, ranging from classic \unix one-liners to modern data-processing scripts;
  (ii) two large and complex use cases for temperature analysis and web indexing;
%% , and container orchestration;
and 
  (iii) two micro-benchmarks inspired by (and comparing with) possible alternatives.
Speedups range between 0.89--61.1$\times$ (avg: $6.7\times$), with the 39 out of 44 scripts seeing non-trivial speedups. 
\sys's runtime primitives add to the base speedup extracted by \sys's program transformations---\eg 8.83$\times$ over a base 5.93$\times$ average for 10 representative \unix one-liners.
%  with \ttt{--width=64}, 
% \kk{eurosys: Readers don't know what --width is here so it might make sense to not mention it.}
% \sys performs better than \ttt{sort --parallel}, a hand-tuned parallel implementation, and GNU parallel, which returns incorrect results if used without care.
\sys accelerates a large program for temperature analysis by 2.52$\times$, parallelizing both the computation (12.31$\times$) and the preprocessing (2.04$\times$) fragment (\ie data download, extraction, and cleanup), which traditionally falls outside of the focus of conventional parallelization systems---even though it takes $75\%$ of the total execution time.
  % extracting 12.31$\times$ from the portion of the program that traditionally falls outside the focus of conventional parallelization systems.
  % \kk{\sys parallelizes the computation by 12.31 and not the preprocessing. It parallelizes the preprocessing by 2.}

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_example2.pdf}}
\begin{minted}[fontsize=\footnotesize,escapeinside=()]{bash}
mkfifo $t{0,1...}
curl $base/$y > $t0 & cat $t0 | split $t1 $t2 &
cat $t1 | grep gz > $t3 & 
cat $t2 | grep gz > $t4 &
...
cat $t9 | sort -rn > $t11 & cat $t10 | sort -rn > $t12 &
cat $t11 | eager > $t13 & cat $t12 | eager > $t14 &
sort -mrn $t13 $t14 > $t15 &
cat $t15 | head -n1 > $out1 &
wait $! && get-pids | xargs -n 1 kill -SIGPIPE
\end{minted}
\caption{
  \textbf{Output of \ttiny{pash --width=2} for Fig.~\ref{fig:example} (fragment).}
  \sys orchestrates parallel execution through named pipes, parallel operators, and custom runtime primitives---\eg \ttiny{eager}, \ttiny{split}, and \ttiny{get-pids}.
}
\vspace{-15pt}
\label{fig:example2}
\end{figure}
